\section{Strings}

The R5RS notion of strings as a distinct type is removed; a Moreso string
is a vector containing only characters.  Moreso has no special restrictions
on what may be done with this kind of string, although some operations,
such as replacing an element with a non-character, will make the object
no longer considered a string.

\subsection{New Procedures}
\begin{entry}{\proto{string?}{ obj}{procedure}}

Returns \schtrue\ if \var{obj} is a vector and every element in \var{obj} is a
character, and \schfalse\ otherwise:

\begin{scheme}
(string? \sharpsign())                    \ev \schtrue
(string? (vector \sharpsign\textbackslash{}c))           \ev \schtrue
(string? (vector \sharpsign\textbackslash{}c \schfalse)) \ev \schfalse
(string? \sharpsign{}t) \ev \schfalse
\end{scheme}
\end{entry}

\begin{entry}{\proto{subvector}{ vector start end}{library procedure}}

{\cf subvector} returns a fresh vector containing the objects in
\var{vector} from index \var{start} (inclusive) to index \var{end}
(exclusive).
\end{entry}

\begin{entry}{\proto{vector-append}{ vector \dotsfoo}{library procedure}}

Returns a vector containing the concatenation of the supplied vectors.
\end{entry}

\begin{entry}{\proto{vector-copy}{ vector}{library procedure}}

Returns a shallow copy of \var{vector}.
\end{entry}

\subsection{Removed Procedures}

The following procedures are removed:
\begin{scheme}
make-string              string-set!
string                   string-ref
string-fill!             string->list
string-length            list->string
string-append            substring
string-copy
\end{scheme}

\subsection{Quoted Literals}

The quoted literal string syntax is kept, except that it is now read as a
vector of characters.  That is,

\begin{scheme}
(vector? "x") \ev \schtrue
(string? "x") \ev \schtrue
(char? (vector-ref "x" 0)) \ev \schtrue
\end{scheme}

{\cf write} renders a string as a quoted literal.

Moreso's {\cf display} writes strings in the same way as R5RS's {\cf display}.

% vim:set ft=tex:
